\LARGE \bf Machine Translation for Tibetan Buddhist Texts

### 2021-04-01 paper/main.tex
Update main.tex
Local commit
Added prelim. Intro

(Kelsey)

>>>>

Our project aims to increase the accessibility of Tibetan religious texts by training a machine translation model specifically to translate religious Tibetan texts to English. We have trained our models in PyTorch and have leveraged the BART architecture in the HuggingFrance transformers library to make the training and architecture more straightforward. By creating thesee models, we hope to motivate scholars to study not only these texts but Tibetan as a whole. Currently, while there has been some interest in machine translation for Tibetan-Chinese and vice versa, the same interest has not been reflected in Tibetan-English machine translation. From a deep dive into the open-source Tibetan NLP material, we were unable to find any projects attempting to translate Tibetan-English nor could we find papers specifically discussing Tibetan-English machine translation. By having a readily available set of translated discourses could create an on-ramp for further language uses because increased access could lead to increased interest, especially in the English-speaking community.
